---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

Load *packages*

```{r}
library(scales)
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(lubridate)
require(forecast)
library(sp)
library(spacetime)
# library(ozmaps)
library(sf)
#library(ggmap)
library(gstat)
library(automap)
library(tsdecomp)
library(lmtest)
library(tseries)
```

Load *data*

```{r}
load("cleaned_data.RData")
```

Let us focus on hourly-summarized air temperature data

```{r}
# Summarize data

air_temp2=air_temp %>% 
  group_by(time=floor_date(time,"1 hour"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

# Inpute NaN values with NA

air_temp2[,-1]=air_temp2[,-1]%>% mutate_all(~ifelse(is.nan(.), NA, .))

# Create vector of equally spaced times

eqdist_times=seq(from=air_temp2$time[1],
                 to=tail(air_temp2$time,1),
                 by="1 hour")

air_temp3=air_temp2%>% 
  right_join(data.frame(time=eqdist_times),by="time")%>%
  arrange(time)

save(air_temp3, file="air_temp3.RData")
```

```{r})
head(air_temp3)
```

```{r}
dim(air_temp3)
```

Summary of the data

```{r}
summary(air_temp3)
```

Put air_temp in long format

```{r}
air_temp_long=air_temp3 %>%
  pivot_longer(!time, names_to = "station", values_to = "air_temperature")
```


Plot each station 

```{r}
par(mfrow=c(4,5),mar=c(1,1,2,1))
for(i in 2:ncol(air_temp3)){
  plot(x=air_temp3$time,y=as.vector(unlist(air_temp3[,i])),type="l",col="black",
       xlab=" ",ylab=" ",
       main=colnames(air_temp3[,i]))
  title(main=colnames(air_temp3)[i])
}
```


Let us have a close look at S24

```{r}
plot(y=air_temp2$S24,x=air_temp2$time, type="l", col="blue", xlab="Time", ylab="Temperature", main="Temperature at S24")
```

```{r}
acf(air_temp2$S24[complete.cases(air_temp2$S24)],lag.max = 24*7, main="ACF of S104")
```

Fit SARIMA model to S24 with period 24. Basic choice for p, q, P and Q (autoregressive and moving average orders for the non-seasonal and seasonal parts) is 1. Possible better choices using AIC or BIC.

```{r}
fit_air24=arima(x=air_temp3$S24, order=c(1,0,1),
                seasonal = list(order=c(1,0,1)
                                ,period=24
                                ,include.mean =T
                                ,method="ML"
                ))
print(fit_air24)
```

Plot residuals against time series.

```{r}
par(mfrow=c(2,1))
plot(air_temp3$time, air_temp3$S24, type="l", col="blue",
     ylab="air temperature",
     xlab="time")
plot(fit_air24$residuals, type="l", col="black",
     ylab="residuals",
     xlab="time")
```

Test stationarity

```{r}
tseries::adf.test(fit_air24$residuals[!is.na(fit_air24$residuals)], alternative = "stationary")
```

Apply Kalman Filter for smoothing

```{r}
kr_sm=KalmanSmooth(air_temp3$S24, fit_air24$model)
id.na <- which(is.na(air_temp3$S24))
y24_sm=air_temp3$S24
for (i in id.na){
  y24_sm[i] <- kr_sm$smooth[i,1]

}

par(mfrow=c(1,1))
plot(x=air_temp3$time,y=y24_sm,type="l",col="blue")
lines(x=air_temp3$time,y=air_temp3$S24,type="l",col="red")
```

Wrap up in a function

```{r}

fill_air_temp=function(air_temp3){
  # air_temp=air_temp %>% 
  #   group_by(time=floor_date(time,"1 hour"))%>%
  #   summarise_if(is.numeric, mean, na.rm = TRUE)
  # 
  # # Inpute NaN values with NA
  # 
  # air_temp[,-1]=air_temp[,-1]%>% mutate_all(~ifelse(is.nan(.), NA, .))
  # 
  # # Create vector of equally spaced times
  # 
  # eqdist_times=seq(from=air_temp$time[1],
  #                  to=tail(air_temp$time,1),
  #                  by="1 hour")
  # 
  # air_temp3=air_temp%>% 
  #   right_join(data.frame(time=eqdist_times),by="time")%>%
  #   arrange(time)
  
  for(i in 2:ncol(air_temp3)){
    fit_air=arima(x=air_temp3[,i], order=c(1,0,1),
                  seasonal = list(order=c(1,0,1)
                                  ,period=24
                                  ,include.mean =T
                                  ,method="ML"
                  ))
    kr_sm=KalmanSmooth(as.numeric(unlist(air_temp3[,i])),
                       fit_air$model)
    id.na <- which(is.na(air_temp3[,i]))
    y24_sm=as.numeric(unlist(air_temp3[,i]))
    for (j in id.na){
      y24_sm[j] <- kr_sm$smooth[j,1]
    }
    air_temp3[,i]=y24_sm
  }
  
  return(air_temp3)
  
}

```

Apply function to air_temp3

```{r}  
air_temp_full=fill_air_temp(air_temp3)
# Long format
air_temp_long=air_temp_full %>%
  pivot_longer(!time, names_to = "station", values_to = "air_temperature")

```

Plot all air temperature stations with for loop

```{r}
par(mfrow=c(4,5),mar=c(2,2,2,2))
for(i in 2:ncol(air_temp_full)){
  plot(x=air_temp_full$time,y=as.vector(unlist(air_temp_full[,i])),type="l",col="red",
       xlab="",ylab="")
  lines(x=air_temp3$time,y=as.vector(unlist(air_temp3[,i])),type="l",col="black",
       xlab="",ylab="",main=colnames(air_temp3[,i]))
  title(main=colnames(air_temp_full)[i])
}
plot(1, type="n", axes=FALSE, xlab="", ylab="")
legend("topright", legend=c("filled","original"), col=c("red","black"), lty=1:1, cex=1.5,lwd=c(3,3))


# add common legend red for filled and black for original in separate plo

```



```{r}
save(air_temp_full, file="air_temp_filled_smooth.RData")
```


