---
title: "Cool Quiet City"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages loading

```{r}
# Load packages
library(scales)
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(lubridate)

library(sp)
library(spacetime)
# library(ozmaps)
library(sf)
#library(ggmap)
library(gstat)
library(automap)


load("cleaned_data.Rdata")

```
## Time range

```{r}
as.Date(range(cozie_train$time))
as.Date(range(cozie_test$time))

as.Date(range(air_temp$time))
as.Date(range(RH$time))
as.Date(range(wind_dir$time))
as.Date(range(wind_speed$time))
as.Date(range(rainfall$time))
```
## Visualitazion of the target variables

```{r}
target_vars=c("q_earphones","q_noise_kind","q_noise_nearby","q_thermal_preference")

par(mfrow=c(2,2))
# ggplot(cozie_train,aes(x=time,y=cozie_train[,target_vars[1]]))+
#   geom_point()+
#   scale_x_datetime(labels = date_format("%y-%m"))+
#   theme_bw()+
#   labs(title=target_vars[1],y=" ",x="Time")
# ggplot(cozie_train,aes(x=time,y=cozie_train[,target_vars[2]]))+
#   geom_point()+
#   scale_x_datetime(labels = date_format("%y-%m"))+
#   theme_bw()+
#   labs(title=target_vars[2],y=" ",x="Time")
# ggplot(cozie_train,aes(x=time,y=cozie_train[,target_vars[3]]))+
#   geom_point()+
#   scale_x_datetime(labels = date_format("%y-%m"))+
#   theme_bw()+
#   labs(title=target_vars[3],y=" ",x="Time")
# ggplot(cozie_train,aes(x=time,y=cozie_train[,target_vars[4]]))+
#   geom_point()+
#   scale_x_datetime(labels = date_format("%y-%m"))+
#   theme_bw()+
#   labs(title=target_vars[4],y=" ",x="Time")

plot(cozie_train$time,cozie_train[,target_vars[1]],
     xlab="Time",ylab=target_vars[1])
plot(cozie_train$time,cozie_train[,target_vars[2]],
     xlab="Time",ylab=target_vars[2])
plot(cozie_train$time,cozie_train[,target_vars[3]],
     xlab="Time",ylab=target_vars[3])
plot(cozie_train$time,cozie_train[,target_vars[4]],
     xlab="Time",ylab=target_vars[4])
```

There is a time window between January and April with no observations. Let us split the data in two parts, one until 2023-01-21 15:00:16 (indexed 614909), and the other starting from 2023-03-27 11:55:01 (indexed 615204).

```{r}
last_date_first_wind=cozie_train$time[614909]
first_date_second_wind=cozie_train$time[615204]
```

# Summarize data

```{r}
weather_summ=function(x,window="30 minutes"){
  
  mean_x=x %>% group_by(time=floor_date(time,window))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)
  sd_x=x %>% group_by(time=floor_date(time,window))%>%
    summarise_if(is.numeric, sd, na.rm = TRUE)
  
  return(list(mean_x=mean_x,sd_x=sd_x))
  
}
```

```{r}
wdn="1 hour"
wdn2="30 mins"

air_temp_wdn=weather_summ(air_temp,window=wdn)
rainfall_wdn=weather_summ(rainfall,window=wdn)
RH_wdn=weather_summ(RH,window=wdn)
wind_dir_wdn=weather_summ(wind_dir,window=wdn)
wind_speed_wdn=weather_summ(wind_speed,window=wdn)

air_temp_wdn2=weather_summ(air_temp,window=wdn2)
rainfall_wdn2=weather_summ(rainfall,window=wdn2)
RH_wdn2=weather_summ(RH,window=wdn2)
wind_dir_wdn2=weather_summ(wind_dir,window=wdn2)
wind_speed_wdn2=weather_summ(wind_speed,window=wdn2)
```

# Maximum variability for 30 mins and 1 hour frequency

```{r}

max(air_temp_wdn$sd_x[,-1],na.rm = T)
max(rainfall_wdn$sd_x[,-1],na.rm = T)
max(RH_wdn$sd_x[,-1],na.rm = T)
max(wind_dir_wdn$sd_x[,-1],na.rm = T)
max(wind_speed_wdn$sd_x[,-1],na.rm = T)

max(air_temp_wdn2$sd_x[,-1],na.rm = T)
max(rainfall_wdn2$sd_x[,-1],na.rm = T)
max(RH_wdn2$sd_x[,-1],na.rm = T)
max(wind_dir_wdn2$sd_x[,-1],na.rm = T)
max(wind_speed_wdn2$sd_x[,-1],na.rm = T)

```

No huge difference between the two, let us keep the 1 hour frequency dataset.

# Air temperature

```{r}
air_temp_wdn_long=air_temp_wdn$mean_x %>%
  pivot_longer(!time, names_to = "location", values_to = "air_temperature")

ggplot(data=air_temp_wdn_long, aes(x=time, y = air_temperature)) + 
  geom_line(color="#9999CC",na.rm = F) + facet_wrap(~location,nrow=6,ncol=3)+
  scale_x_datetime(labels = date_format("%y-%m"))+
  theme_bw()+
  labs(title="Air temperature",y=" ",x="Time")+
  theme(axis.text.x = element_text(size=5),
        axis.text.y = element_text(size=5),
        strip.text = element_text(size=5),
        panel.spacing = unit(.5, 'pt'))

```

# Rainfall

```{r}
rainfall_wdn_long=rainfall_wdn$mean_x %>%
  pivot_longer(!time, names_to = "location", values_to = "rainfall")

ggplot(data=rainfall_wdn_long, aes(x=time, y = rainfall)) + 
  geom_line(color="#9999CC",na.rm = F) + facet_wrap(~location)+
  scale_x_datetime(labels = date_format("%y-%m"))+
  theme_bw()+
  labs(title="Rainfall",y=" ",x="Time")+
  theme(axis.text=element_text(size=5),strip.background=element_blank(),  strip.text.x = element_blank())

```

# Relative humidity

```{r}
RH_wdn_long=RH_wdn$mean_x %>%
  pivot_longer(!time, names_to = "location", values_to = "RH")

ggplot(data=RH_wdn_long, aes(x=time, y = RH)) + 
  geom_line(color="#9999CC",na.rm = F) + facet_wrap(~location,nrow=6,ncol=3)+
  scale_x_datetime(labels = date_format("%y-%m"))+
  theme_bw()+
  labs(title="Relative humidity",y=" ",x="Time")+
  theme(axis.text.x = element_text(size=5),
        axis.text.y = element_text(size=5),
        strip.text = element_text(size=5),
        panel.spacing = unit(.5, 'pt'))

```

# Wind speed

```{r}
wind_speed_wdn_long=wind_speed_wdn$mean_x %>%
  pivot_longer(!time, names_to = "location", values_to = "wind_speed")

ggplot(data=wind_speed_wdn_long, aes(x=time, y = wind_speed)) + 
  geom_line(color="#9999CC",na.rm = F) + facet_wrap(~location,nrow=6,ncol=3)+
  scale_x_datetime(labels = date_format("%y-%m"))+
  theme_bw()+
  labs(title="Wind speed",y=" ",x="Time")+
  theme(axis.text.x = element_text(size=5),
        axis.text.y = element_text(size=5),
        strip.text = element_text(size=5),
        panel.spacing = unit(.5, 'pt'))

```

# Wind direction

```{r}
wind_dir_wdn_long=wind_dir_wdn$mean_x %>%
  pivot_longer(!time, names_to = "location", values_to = "wind_dir")

ggplot(data=wind_dir_wdn_long, aes(x=time, y = wind_dir)) + 
  geom_line(color="#9999CC",na.rm = F) + facet_wrap(~location,nrow=6,ncol=3)+
  scale_x_datetime(labels = date_format("%y-%m"))+
  theme_bw()+
  labs(title="Wind direction",y=" ",x="Time")+
  theme(axis.text.x = element_text(size=5),
        axis.text.y = element_text(size=5),
        strip.text = element_text(size=5),
        panel.spacing = unit(.5, 'pt'))

```

There is a time window in which data is somehow linearly interpolated. 

```{r}
t_breaks = seq(from = ymd_hms(head(air_temp$time,1)), 
               to = ymd_hms(tail(air_temp$time,1)), 
               by = '1 day')

ggplot(air_temp[119076:144963,])+
  geom_line(aes(x=time,
                y=S44))+
  scale_x_datetime(breaks = t_breaks,
                   labels = date_format("%y-%m-%d"))+
  theme_bw()+
  theme(axis.text.x = element_text(size=5),
        axis.text.y = element_text(size=5))
```

From January 1st until January 11th. Let us get rid of these observations.

```{r}
last_date_first_wind=as.POSIXct("2022-12-31 23:59:00 +08")
```

## First window analysis

```{r}
air_temp1=air_temp_wdn$mean_x[air_temp_wdn$mean_x$time<=last_date_first_wind,]
# dim(air_temp1)
# summary(air_temp1)

rainfall1=rainfall_wdn$mean_x[rainfall_wdn$mean_x$time<=last_date_first_wind,]
#dim(rainfall1)
# summary(rainfall1)
# tail(rainfall1)

RH1=RH_wdn$mean_x[RH_wdn$mean_x$time<=last_date_first_wind,]
wind_dir1=wind_dir_wdn$mean_x[wind_dir_wdn$mean_x$time<=last_date_first_wind,]
wind_speed1=wind_speed_wdn$mean_x[wind_speed_wdn$mean_x$time<=last_date_first_wind,]

```

Air temperature

```{r}
apply(air_temp1,2,function(x){sum(is.na(x))/length(x)*100})
```

Drop S117 (all NAs).

```{r}
air_temp1=subset(air_temp1, select = -S117)
```

Rainfall
```{r}
apply(rainfall1,2,function(x){sum(is.na(x))/length(x)*100})
```

Drop S36, S82.

```{r}
rainfall1=subset(rainfall1, select = -c(S36,S82))
```


Relative humidity

```{r}
apply(RH1,2,function(x){sum(is.na(x))/length(x)*100})
```

Wind direction

```{r}
apply(wind_dir1,2,function(x){sum(is.na(x))/length(x)*100})
```

Wind speed

```{r}
apply(wind_speed1,2,function(x){sum(is.na(x))/length(x)*100})
```


# Univariate temporal kriging

The following function performs temporal kriging (needed to "fill the gaps" in the datasets).
```{r}
temp_krige=function(x){
  x_sp=x
  
  temp_grid=1:nrow(x)
  temp_grid=expand.grid(temp_grid,1)
  colnames(temp_grid)=c("indx","knot")
  gridded(temp_grid)=~indx+knot
  
  for(i in 2:ncol(x)){
    #i=17
    x_sp=x[,c(1,i)]
    ind_fill=which(is.na(x_sp[,2]))
    NAcount=sum(is.na(x_sp[,2]))
    
    if(NAcount>0){
      colnames(x_sp)=c("time","z")
      x_sp$indx=1:nrow(x_sp)
      x_sp$knot=1
      x_sp=drop_na(x_sp)
      coordinates(x_sp) <- ~ indx + knot
      
      onedim_krig = autoKrige(z~1, x_sp,temp_grid)
      x[ind_fill,i]=onedim_krig$krige_output$var1.pred[ind_fill]
    }
  }
  return(x)
}
```

$\textbf{Air temperature}$

```{r}
air_temp1_sp=air_temp1

air_temp1_sp$knot=1
air_temp1_sp$indx=1:nrow(air_temp1_sp)

air_temp1_sp.full=temp_krige(air_temp1_sp)
apply(air_temp1_sp.full,2,function(x)sum(is.na(x)))
```

$\textbf{Rainfall}$

```{r}
rainfall1_sp=rainfall1

rainfall1_sp$knot=1
rainfall1_sp$indx=1:nrow(rainfall1_sp)

rainfall1_sp.full=temp_krige(rainfall1_sp)
apply(rainfall1_sp.full,2,function(x)sum(is.na(x)))
apply(rainfall1_sp,2,function(x)sum(is.na(x)))

```

$\textbf{Relative humidity}$

```{r}
RH1_sp=RH1

RH1_sp$knot=1
RH1_sp$indx=1:nrow(RH1_sp)

RH1_sp.full=temp_krige(RH1_sp)
apply(RH1_sp.full,2,function(x)sum(is.na(x)))
apply(RH1_sp,2,function(x)sum(is.na(x)))

```

$\textbf{Wind speed}$

```{r}
wind_speed1_sp=wind_speed1

wind_speed1_sp$knot=1
wind_speed1_sp$indx=1:nrow(wind_speed1_sp)

wind_speed1_sp.full=temp_krige(wind_speed1_sp)
apply(wind_speed1_sp.full,2,function(x)sum(is.na(x)))
apply(wind_speed1_sp,2,function(x)sum(is.na(x)))

```

$\textbf{Wind direction}$

```{r}
wind_dir1_sp=wind_dir1

wind_dir1_sp$knot=1
wind_dir1_sp$indx=1:nrow(wind_dir1_sp)

wind_dir1_sp.full=temp_krige(wind_dir1_sp)
apply(wind_dir1_sp.full,2,function(x)sum(is.na(x)))
apply(wind_dir1_sp,2,function(x)sum(is.na(x)))

```

# Spatial kriging

Define spatial grid

Some considerations:

- Since the cozie app collects data at random time points, does it make sense to consider the temporal dependence of the spatial measurements? Trade-off between accuracy and computational cost

- A quicker approach could involve focusing solely on the time points where the cozie app recorded data, conducting spatial kriging specifically for those observed time instances.

```{r}
LAT=range(locations$latitude)
LON=range(locations$longitude)
step=.001
singapore_grid=expand.grid(lat=seq(LAT[1],LAT[2],by=step),
            lon=seq(LON[1],LON[2],by=step))
```





