---
title: "Cool Quiet City"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages loading

```{r}
# Load packages
library(scales)
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(lubridate)

load("cleaned_data.Rdata")

```
## Time range

```{r}
as.Date(range(cozie_train$time))
as.Date(range(cozie_test$time))

as.Date(range(air_temp$time))
as.Date(range(RH$time))
as.Date(range(wind_dir$time))
as.Date(range(wind_speed$time))
as.Date(range(rainfall$time))
```
## Visualitazion of the target variables

```{r}
target_vars=c("q_earphones","q_noise_kind","q_noise_nearby","q_thermal_preference")

par(mfrow=c(2,2))
# ggplot(cozie_train,aes(x=time,y=cozie_train[,target_vars[1]]))+
#   geom_point()+
#   scale_x_datetime(labels = date_format("%y-%m"))+
#   theme_bw()+
#   labs(title=target_vars[1],y=" ",x="Time")
# ggplot(cozie_train,aes(x=time,y=cozie_train[,target_vars[2]]))+
#   geom_point()+
#   scale_x_datetime(labels = date_format("%y-%m"))+
#   theme_bw()+
#   labs(title=target_vars[2],y=" ",x="Time")
# ggplot(cozie_train,aes(x=time,y=cozie_train[,target_vars[3]]))+
#   geom_point()+
#   scale_x_datetime(labels = date_format("%y-%m"))+
#   theme_bw()+
#   labs(title=target_vars[3],y=" ",x="Time")
# ggplot(cozie_train,aes(x=time,y=cozie_train[,target_vars[4]]))+
#   geom_point()+
#   scale_x_datetime(labels = date_format("%y-%m"))+
#   theme_bw()+
#   labs(title=target_vars[4],y=" ",x="Time")

plot(cozie_train$time,cozie_train[,target_vars[1]],
     xlab="Time",ylab=target_vars[1])
plot(cozie_train$time,cozie_train[,target_vars[2]],
     xlab="Time",ylab=target_vars[2])
plot(cozie_train$time,cozie_train[,target_vars[3]],
     xlab="Time",ylab=target_vars[3])
plot(cozie_train$time,cozie_train[,target_vars[4]],
     xlab="Time",ylab=target_vars[4])
```

There is a time window between January and April with no observations. Let us split the data in two parts, one until 2023-01-21 15:00:16 (indexed 614909), and the other starting from 2023-03-27 11:55:01 (indexed 615204).

```{r}
last_date_first_wind=cozie_train$time[614909]
first_date_second_wind=cozie_train$time[615204]
```

# Air temperature

```{r}
par(mfrow=c(round((ncol(air_temp)-1)/3),3))
for(i in 2:ncol(air_temp)){
  plot(air_temp$time,air_temp[,i],type='l',xlab="time",
       ylab=colnames(air_temp[i]))
}
```

# S100

```{r}
par(mfrow=c(3,2))
plot(air_temp$time,air_temp$S100,type='l',xlab="time",ylab="Air temperature",
     main="S100")
plot(RH$time,RH$S100,type='l',xlab="time",ylab="Relative humidity",
     main="S100")
plot(rainfall$time,rainfall$S100,type='l',xlab="time",ylab="Rainfall",
     main="S100")
plot(wind_dir$time,wind_dir$S100,type='l',xlab="time",ylab="Wind direction",
     main="S100")
plot(wind_speed$time,wind_speed$S100,type='l',xlab="time",ylab="Wind speed",
     main="S100")

```


## First window analysis

```{r}
air_temp1=air_temp[air_temp$time<=last_date_first_wind,]
# dim(air_temp1)
# summary(air_temp1)

rainfall1=rainfall[rainfall$time<=last_date_first_wind,]
dim(rainfall1)
# summary(rainfall1)
# tail(rainfall1)

RH1=RH[RH$time<=last_date_first_wind,]
wind_dir1=wind_dir[wind_dir$time<=last_date_first_wind,]
wind_speed1=wind_speed[wind_speed$time<=last_date_first_wind,]
```

# Function to summarize data by time intervals 

```{r}
weather_summ=function(x,window="30 minutes"){
  
  mean_x=x %>% group_by(time=floor_date(time,window))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)
  sd_x=x %>% group_by(time=floor_date(time,window))%>%
    summarise_if(is.numeric, sd, na.rm = TRUE)
  
  return(list(mean_x=mean_x,sd_x=sd_x))
  
}
```

```{r}
wdn="30 minutes"
#wdn="1 hour"

air_temp1_30mins=weather_summ(air_temp1,window=wdn)
rainfall1_30mins=weather_summ(rainfall1,window=wdn)
RH1_30mins=weather_summ(RH1,window=wdn)
wind_dir1_30mins=weather_summ(wind_dir1,window=wdn)
wind_speed1_30mins=weather_summ(wind_speed1,window=wdn)
```

# Maximum variability for 30 mins frequency

```{r}
max(air_temp1_30mins$sd_x[,-1],na.rm = T)
max(rainfall1_30mins$sd_x[,-1],na.rm = T)
max(RH1_30mins$sd_x[,-1],na.rm = T)
max(wind_dir1_30mins$sd_x[,-1],na.rm = T)
max(wind_speed1_30mins$sd_x[,-1],na.rm = T)
```

# Air temperature

```{r}
air_temp1_long=air_temp1 %>%
  pivot_longer(!time, names_to = "location", values_to = "air_temperature")

ggplot(data=air_temp1_long, aes(x=time, y = air_temperature)) + 
  geom_line(color="#9999CC",na.rm = F) + facet_wrap(~location,nrow=6,ncol=3)+
  scale_x_datetime(labels = date_format("%y-%m"))+
  theme_bw()+
  labs(title="Air temperature",y=" ",x="Time")+
  theme(axis.text.x = element_text(size=5),
        axis.text.y = element_text(size=5),
        strip.text = element_text(size=5),
        panel.spacing = unit(.5, 'pt'))

summary(air_temp1[,-1])

```


