---
title: "Proportional odds ratio"
output: html_document
date: "2024-03-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data loading

```{r}
load("df_train2.Rdata")
#names(df_train)
```

# Thermal comfort

## Data cleaning

Let us consider only variables relevant for thermal comfort assessment.

```{r}
dat=df_train[,c(3:7,8:12,16,21,49,51,53,57)]
dat$q_thermal_preference=ordered(df_train$q_thermal_preference,
                                 levels=c("Warmer","No change", "Cooler"))
```

We want to focus on outdoor thermal comfort, so we consider only observations from individuals who answered "Outdoor" to the question "Where are you?". 
- $\texttt{q_location}$ response to micro-survey question "Where are you?";


```{r}
dat=subset(dat,q_location=="Outdoor")
dat=subset(dat,select=-q_location)
```

Below, a brief description of each variable

```{r}
names(dat)
```

- $\texttt{air_temp}$ (°C);
- $\texttt{rainfall}$ (mm);
- $\texttt{relative_humidity}$ (%);
- $\texttt{wind_speed}$ (knots);
- $\texttt{wind_dir}$ (°);
- $\texttt{ts_stand_time}$ (min);
- $\texttt{ts_step_count}$ (number of steps);
- $\texttt{ts_walking_distance}$ (m);
- $\texttt{ts_heart_rate}$ (beats per minute);
- $\texttt{ts_audio_exposure_environment}$ (dB);
- $\texttt{q_noise_nearby}$ response to micro-survey question "Noise distractions nearby?";
- $\texttt{Green.View.Mean}$ GVF;
- $\texttt{Sky.View.Mean}$ SVF;
- $\texttt{Building.View.Mean}$ Building View Factor;
- $\texttt{Visual.Complexity.Mean}$ Visual Complexity Index.

## Response variable

- $\texttt{q_thermal_preference}$ response to micro-survey question "Thermally, what do you prefer now?".

It is an ordinal variable 

with the following levels

```{r}
head(dat$q_thermal_preference)
```

Summary statistics of the response variable

```{r}
summary(dat$q_thermal_preference)
barplot(table(dat$q_thermal_preference)/length(dat$q_thermal_preference),
        col=rainbow(length(unique(dat$q_thermal_preference))))
```

Dataset dimension

```{r}
dim(dat)
```


Summary statistics of the explanatory variables

```{r}
summary(dat[c("air_temp","rainfall","RH","wind_speed",
              "Green.View.Mean","Sky.View.Mean","Building.View.Mean")])
```

Thermal preferences with respect to location


```{r}
#prop.table(table(dat$q_thermal_preference,dat$q_location),margin = 1)*100
```

Summary statistics of weather variables conditional on thermal preferences

```{r}

library(doBy)
#Air Temperature
summaryBy(air_temp ~ q_thermal_preference, data=dat, FUN=c(mean, sd, min, max))

#Rainfall
summaryBy(rainfall ~ q_thermal_preference, data=dat, FUN=c(mean, sd, min, max))

#Relative humidity
summaryBy(RH ~ q_thermal_preference, data=dat, FUN=c(mean, sd, min, max))

#Wind speed
summaryBy(wind_speed ~ q_thermal_preference, data=dat, FUN=c(mean, sd, min, max))

```

Summary statistics of urban morphology conditional on thermal preferences

```{r}

library(doBy)

#Green View Factor
summaryBy(Green.View.Mean ~ q_thermal_preference, data=dat, FUN=c(mean))

#Sky View Factor
summaryBy(Sky.View.Mean ~ q_thermal_preference, data=dat, FUN=c(mean))

#Building View Factor
summaryBy(Building.View.Mean ~ q_thermal_preference, data=dat, FUN=c(mean))

```

# Combined effect of air temperature and humidity


```{r}
dat2=data.frame(dat,
                air_RH=dat$air_temp*dat$RH)
dat_scaled=apply(dat2[,-c(11,16)],2,scale)
dat_scaled=data.frame(dat_scaled,
                q_noise_nearby=dat$q_noise_nearby,
                q_thermal_preference=dat$q_thermal_preference)

fit_sc=polr(q_thermal_preference~.,data=dat_scaled)
summary(fit_sc)

fit_=polr(q_thermal_preference~.,data=dat)
summary(fit_)

```


## Thermal comfort model

```{r}
library(MASS)
fit=polr(q_thermal_preference~.,data=dat)
```

Estimated coefficients

```{r}
summary(fit)
```



# Acustic comfort

```{r}
dat2=df_train[,c(3:7,8:12,13:14,16,20,22,49,51,53,57)]
dat2$q_noise_nearby=ordered(df_train$q_noise_nearby,
                            levels=c("None","A little","A lot"))
```

Below, a brief description of additional variables

```{r}
names(dat2)
```

- $\texttt{q_alone_group}$ response to micro-survey question "category of activity?";
- $\texttt{q_earphones}$ response to micro-survey question "wearing earphones?";
- $\texttt{q_noise_nearby}$ response to micro-survey question "noise distractions nearby? (without earphones)"

Summary statistics of the additional variables

```{r}
summary(dat2[c("q_alone_group","q_earphones","q_noise_kind")])
```

Barplot of the response variable

```{r}
summary(dat2$q_noise_nearby)
barplot(table(dat2$q_noise_nearby)/length(dat2$q_noise_nearby),
        col=rainbow(length(unique(dat2$q_noise_nearby))))
```

Contingency tables

```{r}
prop.table(table(dat2$q_noise_nearby,dat2$q_location),margin=1)*100
prop.table(table(dat2$q_noise_nearby,dat2$q_alone_group),margin=1)*100

```

Summary statistics of audio exposure conditional on noise level

```{r}
library(doBy)
summaryBy(ts_audio_exposure_environment ~ q_noise_nearby, 
          data=dat2, FUN=c(mean))

```

## Acustic comfort model

We removed $\texttt{q_earphones}$ and $\texttt{q_noise_kind}$ from the set of explanatory variables because their inclusion stopped the model from reaching convergence.

```{r}
library(MASS)
fit2=polr(q_noise_nearby~.,
          data=subset(dat2,select=-c(q_earphones, 
                                     q_noise_kind))
          )
```

Estimated coefficients

```{r}
summary(fit2)
```

<!-- ```{r} -->
<!-- ind1=which(dat2$q_earphones=="Not applicable") -->
<!-- ind2=which(dat2$q_noise_kind=="Not applicable") -->
<!-- sum(ind1!=ind2) -->
<!-- ``` -->

<!-- Let us fit a model considering only individuals not answering "Not applicable" to the above  -->

<!-- ```{r} -->
<!-- dat3=dat2[-ind1,] -->
<!-- dat3$q_earphones=droplevels(dat3$q_earphones) -->
<!-- dat3$q_noise_kind=droplevels(dat3$q_noise_kind) -->
<!-- fit3=polr(q_noise_nearby~., -->
<!--           data=dat3 -->
<!--           ) -->
<!-- ``` -->

<!-- Estimated coefficients -->

<!-- ```{r} -->
<!-- summary(fit2) -->
<!-- ``` -->
