---
title: "SVF and GVF - Milan"
output: html_document
date: "2023-12-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=F)
```

## Data

Data are collected from the Global Urban Network (GUN)
[dataset](https://figshare.com/articles/dataset/Global_Urban_Network_Dataset/22124219).

## Milan

```{r}
library(geojsonio)
library(leaflet)
library(leaflet.extras)
library(dplyr)

milan_nodes=geojson_read("Milan_nodes_100m.geojson",what="sp")
```

Data is available in .geojson format.

# Brief summary statistics

Dataset dimension
```{r}
df=milan_nodes %>% as.data.frame
dim(df)
summary(df[,c("Sky.View.Mean","Green.View.Mean")])
```

Histograms of the relevant variables
```{r}
par(mfrow=c(1,2))
hist(df$Sky.View.Mean,xlab=" ", ylab=" ", main="Sky View Factor",col="cyan")
hist(df$Green.View.Mean,xlab=" ", ylab=" ", main="Green View Factor", col="green")
```

There is no spatial point with SVF greater than 0.8, as the maximum observed value is 0.67. For this reason, we consider the following scenarios

1) $SVF>0.6$
2) $SVF<0.4$  and $GVF<0.2$
3) $SVF<0.4$ and $GVF>0.6$

```{r}
FirstScen=df[which(df$Sky.View.Mean>.6),c("x","y","Sky.View.Mean")]
FirstScen$Scen=as.factor(1)
SecondScen=df[which(df$Sky.View.Mean<.4&df$Green.View.Mean<0.2),
              c("x","y","Sky.View.Mean","Green.View.Mean")]
SecondScen$Scen=as.factor(2)
ThirdScen=df[which(df$Sky.View.Mean<.4&df$Green.View.Mean>0.6),
             c("x","y","Sky.View.Mean","Green.View.Mean")]
ThirdScen$Scen=as.factor(3)
df2=full_join(FirstScen,SecondScen)
df2=full_join(df2,ThirdScen)
```

Points satisfying the first condition $SVF>0.6$
```{r}
dim(FirstScen)
```

Points satisfying the second condition $SVF<0.4$  and $GVF<0.2$
```{r}
dim(SecondScen)
```

Points satisfying the third condition $SVF<0.4$ and $GVF>0.6$
```{r}
dim(ThirdScen)
```


Interactive map
```{r}
pal <- colorFactor(c("blue","red", "darkgreen"), domain = c("1", "2","3"))
colnames(df2)[1:2]=c("long","lat")
leaflet(df2) %>% addTiles() %>%
  addCircleMarkers(
    radius = 2.5,
    color = ~pal(Scen),
    stroke = FALSE, fillOpacity = 0.5
  )
```


